\vskip-0.6in Temporary Trade Barriers: When Will They End?

### 2017-11-06 draft.tex
fix small typos in appendix
add assumption on dist'n of theta

@@

$ZN(\bta,\tad)$ is also always positive on $[0,\tau^O]$ since $\tad > \tau^a$ and on this range $\tad$ is closer to the optimum. Profits are increasing in $\tad$, so the second summand is positive on $[0,\tau^O]$. With a positive denominator, we thus have that the entire express is positive on $[0,\tau^O]$.

>>>>

\begin{assumption}
  $\ta$ is uniformly distributed on some $\Theta=\left[\underline{\ta},\overline{\ta}\right]$.
  \label{as:ta}
\end{assumption}

@@

$ZN(\bta,\tad)$ is also always positive on $[0,\tau^O]$ since $\tad > \tau^a$ and on this range $\tad$ is closer to the optimum. Profits are increasing in $\tad$, so the second summand is positive on $[0,\tau^O]$. With a positive denominator, we thus have that the entire expression is positive on $[0,\tau^O]$.
